### 2015-12-24 extended-abstract.tex
change title, proof 1st 2 paragraphs, add to outline

\begin{document}
\begin{center}
  Temporary Trade Barriers: How Long Do They Last?\\
	Kristy Buzard
\end{center}

\vskip.2in
Today's world trading system is largely governed by a system in which countries commit to tariff bindings and yet raise their tariffs above those bindings through a variety of temporary trade barriers (TTBs) on a not-infrequent basis (Bown 2011). A significant literature has explored the question of which industries receive protection through TTBs and under what conditions. This project asks a related but distinct question: given that a product receives protection, what determines the length of that protection? \\

This question can be addressed in the context of renewals of trade remedies under the WTO agreements. Normally, temporary measures such as anti-dumping and counter-vailing duties have a five-year sunset provision that is subject to renewal by the U.S. International Trade Commission. Conditional on a TTB being granted and applied for five years, one would like to know what determines whether a renewal order is granted so that it continues in force.

@@

\vskip.3in
\begin{itemize}
	\item If lobbies have to exert effort to achieve higher-than-MFN tariffs, when will it be worthwhile for them to do so?
\end{itemize}

>>>>

\begin{document}
\begin{center}
  Temporary Trade Barriers: When Will They End?\\
	Kristy Buzard
\end{center}

\vskip.2in
Today's world trading system is largely governed by a system in which countries commit to tariff bindings and yet raise their tariffs above those bindings through a variety of temporary trade barriers (TTBs) on a not-infrequent basis (Bown 2011). A significant literature has explored the question of which industries receive protection through TTBs and under what conditions this happens. This project asks a related but distinct question: given that a product receives protection, what determines the duration of the protection it receives? \\

This question can be addressed in the context of renewals of trade remedies under the WTO agreements. Normally, temporary measures such as anti-dumping and counter-vailing duties are imposed with a five-year sunset provision that is subject to renewal by the U.S. International Trade Commission. Conditional on a TTB being granted and applied for five years, one would like to know what determines whether a renewal order is granted so that it continues in force. \\

Set up model
\begin{itemize}
	\item Take trade agreement tariff as given
	\item Lobby exerts effort to convince ITC to apply anti-dumping duties (AD determined endogenously)
\end{itemize}

@@

\vskip.3in
\begin{itemize}
	\item If lobbies have to exert effort to achieve higher-than-MFN tariffs, when will it be worthwhile for them to do so?
	\item It's about how hard the lobby lobbies, how much reaction they get
\end{itemize}
